### 2018-07-06 submission/supplemental.Rmd
change table orders

**Table S2: ANOVA results of differences in number of OTUs between polymerases in fecal and mock samples**

@@

@@

**Table S3: Tukey post-hoc results of differences in number of OTUs between polymerases in fecal and mock samples**

@@

**Table S4: Kruskal-Wallis results of differences in error rate, sequences with an error, and chimera prevalence between polymerases in mock samples**

**Table S5: Dunn's Post-Hoc results of differences in error rate, sequences with an error, and chimera prevalence between polymerases in mock samples**

```{r supplemental_table6, echo=FALSE, message=FALSE, warning=FALSE}

>>>>

**Table S2: Kruskal-Wallis results of differences in error rate, sequences with an error, and chimera prevalence between polymerases in mock samples**

```{r supplemental_table2, echo=FALSE, message=FALSE, warning=FALSE}

**Table S3: Dunn's Post-Hoc results of differences in error rate, sequences with an error, and chimera prevalence between polymerases in mock samples**

@@

**Table S4: ANOVA results of differences in number of OTUs between polymerases in fecal and mock samples**

@@

**Table S5: Tukey post-hoc results of differences in number of OTUs between polymerases in fecal and mock samples**

@@
